%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------


\namesection{Abhinav}{Kumar}{ % Your name
\href{mailto:abhinavkumar580@gmail.com}{abhinavkumar580@gmail.com} | +91 9113724912 % Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{Siliguri Institute of \newline Technology }

\descript{B.Tech in Computer Science \& Engineering}
\location{July 2017 - June 2021 \\ West Bengal, India } 
CGPA - 8.82


\sectionspace % Some whitespace after the section

%------------------------------------------------
\subsection{DAV Public School \\ Khalari}
\descript{Higher Secondary Certificate}
\location{May 2015 - March 2017 \\ Jharkhand, India}
PERCENTAGE - 76.40
\newline
%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Projects}


%------------------------------------------------

\subsection{\href{https://video-meetx.herokuapp.com/}{Video MeetX}}
Basic Video conferencing web app developed using \textbf{NodeJs} and \textbf{SocketIO} that lets you stay in touch with all your friends. This lets you share your screen over the internet. Hosted it on Heroku platform.
\sectionspace

\subsection{\href{https://github.com/abhinav580/aura}{AURA}}
Community website for GDG Siliguri, \\ for managing events, registrations, sponsorships, etc. Used an open \\ source template and integrated \\ various  platforms like meetup.com,\\ twitter, etc. Used \textbf{Nodejs}  Angular for \\ this project.
\sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{Programming}

Typescript \textbullet{} Javascript \textbullet{} NodeJs \textbullet{} GoLang \textbullet{} PostgreSQL \newline


\subsection{Tools/Applications}
GIT \textbullet{} Docker \textbullet{} Visual Studio Code \textbullet{} Postman

\sectionspace
\subsection{Cloud}
AWS

\sectionspace % Some whitespace after the section
%------------------------------------------------
% Links
%------------------------------------------------

\section{Links} 

GitHub: \href{https://github.com/abhinav580}{github.com/abhinav580} \\
LinkedIn: \href{https://www.linkedin.com/in/abhinav580/}{linkedin.com/in/abhinav580/}  \\
HackerEarth: \href{https://www.hackerearth.com/@abhinavkmr580}{@abhinavkmr580} \\



\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}
\sectionspace
\runsubsection{McAfee}
\descript{| Software Development Engineer}

\location{July. 2021 – present | Bangalore, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Developed scalable back-end APIs which is used to handle orders and subscriptions for McAfee products.  
\item Worked on multiple orchestration services using \textbf{NodeJs} for Provisioning Subscriptions and Entitlements.
\item Worked on Subscription Migration project for migrating active/expired subscriptions and past transactions from legacy system to new system. Independently worked on development of this service keeping business use cases in mind. Made sure that its a seamless transition for a user.
\item Worked on Account Migration project for migrating customers from legacy system to new system. I worked on various data services, functional services as well as orchestration services.
\item Organize and handle bugs and issues reported, continuously update applications to meet the needs.
\item Improved the performance by 2x compared to legacy systems by using micro services architecture.
\item Integrated legacy system support within the new micro services for backward compatibility so that existing flows doesn't breaks.
\item Primarily used \textbf{NodeJs} for most of the services and occasionally worked on some data and functional services using \textbf{GoLang \& PostgreSQL}.
\end{tightitemize}

\sectionspace % Some whitespace after the section
\sectionspace
%------------------------------------------------
\runsubsection{McAfee}
\descript{| Technical Intern}

\location{February 2021 – June 2021 | Bangalore, India}
\begin{tightitemize}
\item Worked on Email-Masking orchestration project and implemented some key functionalities like \textbf{integrating events}.
\item Wrote end to end unit tests using \textbf{Jest} and made sure that the code coverage is 100\% for all the layers.
\item Wrote end to end \textbf{Postman Collections} and test cases so that anyone can use/test the service with one click.

\end{tightitemize}

\sectionspace % Some whitespace after the section
\sectionspace
%------------------------------------------------
\runsubsection{ZS Associates}
\descript{| Business Technology Analyst Intern}

\location{Oct 2020 – Jan 2021 | Pune, India}
\begin{tightitemize}
\item Worked on Data Quality Management for Pharmaceutical data sets.
\item Worked on various Proof of Concepts(POCs) with Big Data Research \& Development team.
\item Wrote Python scripts to manage airflow workflows.

\end{tightitemize}

\sectionspace % Some whitespace after the section
\sectionspace




%------------------------------------------------
% Research
%------------------------------------------------

%------------------------------------------------



%------------------------------------------------
% Awards
%------------------------------------------------

\section{Achievements } 
\sectionspace

\begin{tightitemize}
\item Got selected as an organiser for Google Developer Groups (GDG) \\      Siliguri chapter.
\item Won the first level and got qualified for Grand Finale of Smart India \\ Hackathon - 2020.
\item Awarded with the title of Intel Software Innovator by \textit{Intel}

\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Societies
%------------------------------------------------

%\section{Membership} 

%\begin{tabular}{rll}
%2011-2015 & Alpha Kappa Lambda Fraternity\\

%\end{tabular}

%\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}
